\pdfminorversion=7
\documentclass[../main.tex]{subfiles}
\begin{document}
\chapter{Acknowledgements}

First and foremost, I would like to express my gratitude to my main
supervisor, Rakesh Kumar, for his continuous support over the
years. He has been an inspirational figure throughout the thesis
writing journey and I am grateful for him never stopping to believe in
me, always being supportive of my ideas, and proposing numerous
interesting opportunities that made my PhD journey what it
was. Furthermore, I would like to thank my co-supervisors Magnus Jahre
and Magnus Själander. In particular, my deepest gratitude goes to
Magnus Jahre for his invaluable support, feedback, ideas, and
encouragement during the final phases of the thesis process.

I would like to thank my colleagues for making my time at IDI a great
one! In particular, I would like to mention Joseph, Björn, Fatemeh,
Lukas,Roman, Bart, Pauline, Arthur, and Özlem for the good times,
enjoyable conversations and entertaining lunches.

I would also like to thank my colleagues I met during my stay at the
PARSA lab at EPFL at the beginning of my PhD. In particular, I would
like to thank Babak Falsafi for accepting me for the opportunity. You
were all highly inspirational and provided motivation and inspiration
for continuing the PhD journey.

For igniting my interest in following a research path and giving me
faith that I could do it, I owe my deepest gratitude to my former
master's thesis advisors from the University of Copenhagen, Brian
Vinter, and Kenneth Skovhede. Your support and encouragement were
invaluable and I would not be here without you! Additionally, I would
like to thank my other colleagues and friends from the now-defunct
eScience group at the Niels Bohr Institute at the University of
Copenhagen for lots of great times and fun Friday beers at Søernes
Ølbar.

To my other friends from the Computer Science department at the
University of Copenhagen, in particular Henrik, Ben, Oleks, Michael,
Troels, Ida, Joachim, Christian, Martin, Morten, Klaus, Karl, and
Alberthe -- thank you so much for being a steady part of my life
throughout the years, being a constant source of support and sharing
countless wonderful experiences.

My most loving and most heartfelt gratitude and appreciation goes to
Gala who is my greatest source of inspiration and support. Your
unwavering love, support, and persistent belief in me was my greatest
asset in this journey. Even during difficult times, you always
encouraged me to keep going and reassured me that I could do it.

Finally, my warmest gratitude goes to my parents, Bente and Bjørn. and
my brother, Mads, for their loving support and encouragement both to
start and complete this journey and throughout my life. Long before
starting this journey, you were my greatest role models, and sources
of persistent inspiration, support, and love. I am forever grateful
for the solid foundation you gave me in life. I am also deeply
grateful for my uncle, Geir, and his valuable insights and support
both in life and the thesis journey

\newpage
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% TeX-command-extra-options: "-shell-escape"
%%% End